Spectral Variability of Two Rapidly Rotating Brown Dwarfs: \\2MASS~J08354256$-$0819237 and 2MASS~J18212815+1414010

### 2017-03-08 ms.tex
I updated the appendix.

We show the original light curves used in model fitting in Figure \ref{fig:tserNoDetrend}.
The linear baseline terms as a function of time and airmass in Equation \ref{eq:cosfit} fit the baseline variations not due to the brown dwarf variations.

>>>>

We show the original light curves used in model fitting in Figure \ref{fig:tserNoDetrend}.
The original light curves show significant variations as a function of time and airmass.
Our sinusoidal model using Equation \ref{eq:cosfit} is shown for each of the light curves in Figure \ref{fig:tserNoDetrend}.
For \ref{fig:tserDetrend} we remove the fit the baseline variations to show the astrophysical modulations due to brown dwarf rotation.
